\textbf{Optimization of Porous Silicon Gradient Refractive Index Structures.}

### 2020-10-22 paper.tex
Coloque las bibliografias en un bib y coloque las modificaciones de la Dra

\documentclass{article}
\usepackage{amsmath}
\usepackage{graphicx} % gráficos
\usepackage[noblocks]{authblk}
%\usepackage{authblk}
%\usepackage[•]{•}ckage{float}
%\usepackage{cite}% para contraer referencias
%\usepackage[usenames]{color}
%\usepackage{showkeys}
\usepackage{bm}
\usepackage{hyperref}
\usepackage[normalem]{ulem} %opcional para la correcciones
\newcommand{\abs}[1]{\lvert#1\rvert}
\usepackage{xcolor}
\newif{\ifinclude}
\newcommand{\notaL}[1]{{\color{blue}+L:#1+}}
\newcommand{\notaC}[1]{{\color{green}+C:#1+}}
\newcommand{\notaV}[1]{{\color{red}+V:#1+}}

@@

\begin{abstract}
We propose a simple setup which that the calculation of the current
density as a function of position within an electrochemical cell used
to produce porous Silicon structures with a controlled gradient in their
index of refraction. We produced samples under several conditions and
characterized them with scanning electron microscopy, and
ultraviolet-visible-near infrared reflectance spectroscopy. Our
results allow us to obtain from experiments on a single or just a few
samples a full characterization of the dependence of porosity,
dielectric function and speed of attack on the current density and on
position, so that novel nonhomogeneous devices may be designed and
built.

Keywords: Porous Silicon; GRIN; Reflectance Spectra.
\end{abstract}
\notaL{Cambié el abstract, pero habrá que revisarlo después.}

\notaV{Surfaces with gradient in refractive index has attracted attention due
 ti its ability to unpair the relation between the shape of the optical 
lens with its optical response. In spite of its possible usage in 
different kinds of devices and applications, it still remains
desirable to predesign GRIN structures with spacial predictability 
of electrochemical gradients.  In this work we report}

\section{Introduction}
\label{sec:introduction}
\notaV{$
Introduction

Surfaces with gradient in the refractive index (GRIN) are of 
importance not only due to the possibility of being able to 
engineer/tune the propagation of light within the structure’s 
surface for applications such as flat lenses, but also for several 
interesting biological applications where the continual topographical 
variation is being exploited [X]. As an example, roughness dependent 
response of the cells has been tested on such materials for applications 
in medical implants [Y].   Gradients have also been employed for several 
technological applications such as high-yield screening of catalysts, 
sensing materials and biomolecules [W. F. Maier, K. Stçwe, S. Sieg, Angew. 
Chem. 2007, 119, 6122; Angew. Chem. Int. Ed. 2007, 46, 6016. ;  S. Jayaraman, 
A. C. Hillier, J. Comb. Chem. 2004, 6, 27; S. Jayaraman, A. C. Hillier, Meas. 
Sci. Technol. 2005, 16, 5. ; R. A. Potyrailo, V. M. Mirsky, Chem. Rev. 2008, 108, 770.]

Apart from some methods developed by S.E. Fosdick et al [JACS  2010, 132, 9226-9227], 

@@

on gold electrode have been made by Shannon’s group[].  Among the electrochemical methods, 
compositional and doping density changes in the conducting polymer have been used to 
produce the gradients using Indium tin oxide electrode [S. Inagi, Y. Ishiguro et al 
Angew Chem Int. Ed. 2010, 49, 10136-10139; Angew Chem 2010 122, 10334-10337].   

@@

reactions and gradient doping of the polymers [Gradient Doping of Conducting Polymer 
Films by Means of Bipolar Electrochemistry Y. Ishiguro, S. Inagi, and T.Fuchigami 
Langmuir 2011 27 (11), 7158-7162].   (PENDING : few MORE EXAMPLES from last couple of years)

@@

with VLSI devices & integrable with microelectronics, for the fabrication 

@@

electrode configuration in the electrochemical synthesis of porous silicon [].  

@@

chemical and biosensor [Porous Silicon Fabry–Pérot Interferometer for
N-Acetyl-β-d-Glucosaminidase Biomarker Monitoring  D. Nanda Kumar, 
Nofar Pinker, and Giorgi Shtenberg  ACS Sensors 2020 5 (7), 1969-1976; DOI: 
10.1021/acssensors.0c00348], microelectronics and MEMS[xx], as well as a 
range of optical[XXX] and optoelectronic applications[XXX].  Specifically, 

@@

[xxX] of 1D photonics crystals. 

@@

with a lateral gradient (in terms of optical thickness/ pore size and t
hickness of the porous layer) has also been exploited for different applications 
[REF… ]. In this configuration, a small platinum electrode (cathode)  

@@

density  with an increase in the distance from the electrode \cite{I102, I103}. 

@@

to  few micrometers  \cite{I104}. The range of the dimensions of the pores and 

@@

in 2002 \cite{I101} applied it for the determination of protein size. 

@@

 optical filters (multilayered structures) with lateral gradient 
 [Li, Yang Yang, Peter Kim, and Michael J. Sailor. 
 "Painting a rainbow on silicon–a simple method to 
 generate a porous silicon band filter gradient.
 " physica status solidi (a) 202.8 (2005): 1616-1618.] for 
 developing ethanol sensor (Sailor 2012...). Additionally it 
 has been shown that the combination of thermal  oxidation  and 

@@

optical elements from PS \cite{I16}.    Kruger et al showed 
the ...  [ Krueger, Neil A., et al. "Porous silicon gradient 
refractive index micro-optics." Nano letters 16.12 (2016): 7402-7407.] 
In addition the same group ...[Krueger, Neil A., et al. 
 "Electrochemical Fabrication of Flat, Polymer‐Embedded 
Porous Silicon 1D Gradient Refractive Index Microlens 
Arrays." physica status solidi (a) 215.13 (2018): 1800088].  

@@

radial interfacial potential distribution (Wang, Joanna, 
Michael J. Sailor, and Byoung‐Yong Chang. "Fabrication of a lateral 
gradient rugate in porous silicon for a miniature spectrometer
application." ChemElectroChem 6.24 (2019): 5967-5972. On the other 
hand, the effect of different topographical features present on the 
same chip, has also been used to culture / adhesion of certain cells \cite{I14}

@@

evaluated parameters . Finally,  the conclusions are given in Section X

$}

\notaV{$ Painting a rainbow on silicon - A simple method to 
\notaV{generate a porous silicon 
band filter gradient. / Li, Yang Yang; Kim, Peter; Sailor, Michael J.
In: Physica Status Solidi (A) Applications and Materials Science, 
Vol. 202, No. 8, 06.2005, p. 1616-1618.  (https://doi.org/10.1002/pssa.200461200)

Electrochemical Preparation of Pore Wall Modification Gradients 
across Thin Porous Silicon Layers
Corrina M. Thompson, Michel Nieuwoudt, Anne M. Ruminski, 
Michael J. Sailor, and Gordon M. Miskelly
Langmuir 2010 26 (10), 7598-7603
DOI: 10.1021/la904408h

 Richardson, Kathleen A., et al. "Advances in infrared gradient 
 refractive index (GRIN) materials: a review." Optical Engineering 59.11 (2020): 112602.

Lavanant, Enora, et al. "Radial gradient refractive index 
(GRIN) infrared lens based on spatially resolved crystallization 
of chalcogenide glass." Optical Materials Express 10.4 (2020): 860-867.
While widely used in the visible, radial gradient refractive 
index (GRIN) lenses are still elusive in the IR waveband. 
In this paper we introduce a new method based on spatially
resolved crystallization of chalcogenide glass to produce such lenses. 
Optical and structural

Yoon, Sun Mi, et al. "Subwavelength Hollow-Nanopillared Glass 
with Gradient Refractive Index for Ultralow Diffuse Reflectance 
and Antifogging." ACS applied materials & interfaces 12.5 (2020): 6234-6242.
Nanostructured glass with subwavelength hollow nanopillars 
of diameters of sub-65 nm was fabricated, showing high optical 
transmittance and ultralow diffuse reflectance. A simple
process involving single-step plasma etching was used on a 
glass slide coated with a SiO2...

Perez, Julius C., Tahmid H. Talukdar, and Judson D. Ryckman. 
"Patterning Refractive Index on the Surface of a Chip by Direct 
Nanoimprinting." CLEO: QELS_Fundamental Science. Optical Society of America, 2020.

Szymanowski, Hieronim, et al. "Thin SiNC/SiOC Coatings with a 
Gradient of Refractive Index Deposited from Organosilicon Precursor." Coatings 10.8 (2020): 794.

Perez, Julius C., Tahmid H. Talukdar, and Judson D. Ryckman.
 "Patterning Refractive Index on the Surface of a Chip by Direct 
 Nanoimprinting." CLEO: QELS_Fundamental Science. Optical Society of America, 2020.

$
}

@@

We assume that our electrolytic cell has the shape of a rectangular
prism (see Fig. \ref{f:celda}) with a horizontal base of sides $a$ and $b$, and
filled with the electrolyte up to a height $c$. We assume that the
walls of the cell are insulating while the bottom is completely
covered with the sample, which is an
electrically grounded relatively good conductor. Within the electrolyte we position an electrode
which we assume is a thin conducting wire, insulated from the electrolyte
but for a small tip, which we approximate as a
point current source.
\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{celdan1}
  \caption{Prism shaped electrolytic cell with a rectangular base of
    sides $a$, $b$ filled with electrolyte up to a height $c$. The
    walls of the cell are insulating and the bottom is completely
    covered by the sample, which is assumed to be a good
    conductor. The tip of the electrode is a thin insulated wire
    with just the tip uncovered and located at $\bm r_0=(x_0,y_0,z_0)$ within the
    liquid. The current flows through the electrolyte from the sample
    to the tip.}
  \label{f:celda}
\end{figure}
Within the electrolyte the current density is
\begin{equation}
  \label{eq:j}
  \bm j=\sigma\bm E,
\end{equation}
with
$\sigma$ the conductivity, $\bm E=-\nabla\phi$ the electric field,
and $\phi$ the electric potential. In a
stationary situation
$\nabla\cdot \bm j = \sigma\nabla\cdot\bm E=0$. Thus, the potential
obeys Laplace's equation within the electrolyte,
\begin{equation}
  \label{eq:laplace}
\nabla^{2} \phi=0.
\end{equation}
Consider now an arbitrary closed surface
$\mathcal S$
within the electrolyte that surrounds completely the tip of the
electrode. Integrating $ \bm j$ over this surface we obtain
\begin{equation}
  \label{eq:I}
\int_{\mathcal S'} d\bm a \cdot \bm j = -I,
\end{equation}
where the prime on $\mathcal S'$ means we remove from the surface a
very small hole through which the wire that feeds the current to the
electrode gets
through, and the sign is consistent with the current direction in
Fig. \ref{f:celda}. Assuming the wire is narrower than any other relevant
distance in the system, we may interpret Eq. \eqref{eq:I} as an
integral over a closed surface of the current \eqref{eq:j} within the
electrolyte, ignoring the actual current within the wire. Thus
\begin{equation}
  \label{eq:gauss}
  \int_{\mathcal S} d\bm a \cdot \bm E = -\frac{I}{\sigma}
\end{equation}
Using Gauss's law, we interpret this equation as a source for the
potential in the form of a point charge
\begin{equation}
  q_0 = -\frac{I}{4 \pi \sigma}
\end{equation}
at the position $\bm r_0=(x_0, y_0, z_0)$ of the
tip of the electrode. Note that $q_0$ would be the total charge,
and it shouldn't be further screened through the permittivity of the
electrolyte.

@@

This problem may be solved readily using image charge theory \cite{T1,T2}.

@@

The electrostatic potential produced by an infinite array of
charges expressed as a sum in real space of Coulomb terms has ill
convergence properties. The potential can be obtained
using the Ewald summation technique \cite{T3,T4,T5}, which yields
two rapidly converging series, one in real space and another one in reciprocal space.
Nevertheless, as we need the potential and the field to obtain the
current density on the surface of the sample on which  no
real nor image charges lie, we may perform a somewhat simpler planewise
summation, where we first obtain the potential and field produced by a
simple periodic lattice of charges using a fast convergent sum over the 2D
reciprocal vectors, then sum over the charges that form the basis
of the 2D {\em crystal} plane, and finally sum over all the
 planes \cite{T6,T7}.\notaL{¿Estas referencias son relevantes? ¿En verdad
   se define en ellas la suma de Ewald por planos? Dime dónde p.f., en qué
   página. Y checa que todas las referencias tengan que ver con lo que decimos}

@@

In Fig. \ref{fig:DE1} we show a schematic representation of our
experimental setup to manufacture GRIN PS structures.
As dicussed above, we fabricated an electrolytic cell with the shape of a
rectangular prism on the bottom of which we place a Si wafer which makes
electrical contact to a gold plate \notaL{Lo inventé; de qué material es
  el contacto bajo la muestra?} which together make the anode. The
cathode consists of a platinum wire insulated except for a small region
at its tip, which we take as a point current drain.
We also show a schematic drawing of the expected GRIN PS structures,
with a gradient in the porosity, and in the thickness, density and depth
of the resulting pores.

\subsection{Fabrication of GRIN  PS Single Layers}
\label{sec:fabrication-ps-grin}
We manufactured single layer PS structures through electrochemical
anodization of a (100) $p$-type crystalline Si wafer
(resistivity 0.002 - 0.005 $ \Omega\,\text{cm}$), under galvanostatic
conditions. The process was performed at
room temperature,\notaL{OJO. No controlaste la temperatura} with an
electrolytic mixture of aqueous hydrofluoric
acid (HF) (concentration 48\% wt), glycerol (purity 99.8 \% wt) and
ethanol (purity 99.9\% wt) in a 3:7:1 volume ratio. \notaL{Checa que
  todo esto sí corresponda a tus últimas muestras} After the
anodizing process, the samples were rinsed with
ethanol (purity: 99.9 $ \% $  wt). The electrolytic cell had the shape
of a rectangular prism as shown in Fig. \ref{fig:DE1}, with a base of
sides $a=2.01\,\text{cm}$ \notaL{Cambié el número, de acuerdo a unas
  mediciones de Cristian} and $b=1.48\,\text{cm}$, with an uncovered sample area
of about $3\,\text{cm}^2$. The height of the liquid was set at
$c=1\,\text{cm}$. The cathode was a
platinum wire that with a diameter of $0.41\,\text{mm}$ insulated by a
teflon cylinder of external diameter $\,2\text{mm}$, with an uncovered
tip located at $\bm r_0=(x_0,
y_0,z_0)=(0.2\,\text{cm},0.74\,\text{cm},0.9\,\text{cm})$. \notaL{Checa todos estos datos}
We manufactured three samples $G_1$, $G_2$ and $G_3$ by applying a
current $I_1=5\,\text{mA}$, $I_2=10\,\text{mA}$ and
$I_3=20\,\text{mA}$, respectively, during a time of $t=250s$.

\subsection{Reflectance Measurement}
\label{sec:refl-meas}
We measured the reflectivity spectra at different positions over our
samples using a {\em Perkin Elmer Lambda 950}
UV-Vis-NIR spectrophotometer.\notaL{Finalmente, ¿fue éste el que se
  usó? Si sí, ¿hay algo internesante que decir sobre el? Cosas como el
tamaño de mancha, resolución espectral, etc.} For interpretation of the
data layer we used
the standard formula \cite{T8,T9} for the reflectance of three media:
air (0) environment, the PS film (1) and the c-Si substrate (2),
 \begin{equation}\label{Eq:ECMR}
   R=\left |\frac{r _ {_ {01}}r _ {_ {12}} e^{2i\psi}}{1+r _ {_
   {01}}r _ {_ {12}} e^{2i\psi}}\right |^2
\end{equation}
where $r_{01}$ and $r_{12}$ are the Fresnel reflectance
coefficients of the air/PS and PS/c-Si interfaces \cite{T10,T11}
and $\psi=k_1^\perp d$, where $k_1^\perp$ is
the component of the wavevector perpendicular to the surface within
the porous layer of thickness $d$. The reflectance depends on the
thickness of the film and on the index of refraction $n_1=n_{\text{PS}}$ of the porous
layer, which we relate to the porosity through Bruggeman's
effective medium theory \cite{I20},
\begin{equation}\label{Eq:Brugg}
 p\frac{1-\epsilon_1} {1+\epsilon_1} + (1-p)
  \frac{\epsilon_2 - \epsilon_1}
  {\epsilon_2+\epsilon_1}=0,
\end{equation}
where $\epsilon_2=\epsilon_{\text{Si}}$ is the dielectric function of
the c-Si substrate, and
$\epsilon_1=n_{\text{PS}}^2$ is the dielectric function of the PS layer.
We fitted the reflectance spectra using the porosity $p$ and the
thickness $d$ and a scale calibration factor $s$ as fitting
parameters, and thus, we obtained the porosity
$p$ and the etching rate $v=d/t$ for different values of the local
current density $j_\perp$ expected at several positions on different
samples.

>>>>

\documentclass{article}
\usepackage{amsmath}
\usepackage{graphicx} % gráficos
\usepackage[noblocks]{authblk}
%\usepackage{authblk}
%\usepackage[•]{•}ckage{float}
%\usepackage{cite}% para contraer referencias
%\usepackage[usenames]{color}
%\usepackage{showkeys}
%\usepackage{ieeetr}
\usepackage{bm}
\usepackage{hyperref}
\usepackage[normalem]{ulem} %opcional para la correcciones
\newcommand{\abs}[1]{\lvert#1\rvert}
\usepackage{xcolor}
\newif{\ifinclude}
\newcommand{\notaL}[1]{{\color{blue}+L:#1+}}
\newcommand{\notaC}[1]{{\color{green}+C:#1+}}
\newcommand{\notaV}[1]{{\color{red}+V:#1+}}

@@

\begin{abstract}
We propose a simple setup which that the calculation of the current
density as a function of position within an electrochemical cell used
to produce porous Silicon structures with a controlled gradient in their
index of refraction. We produced samples under several conditions and
characterized them with scanning electron microscopy, and
ultraviolet-visible-near infrared reflectance spectroscopy. Our
results allow us to obtain from experiments on a single or just a few
samples a full characterization of the dependence of porosity,
dielectric function and speed of attack on the current density and on
position, so that novel nonhomogeneous devices may be designed and
built.
\notaV{ABSTRACT :  Surfaces with the gradient in the refractive index 
have attracted attention due to their ability to unpair the relation
 between the shape of the optical lens with its optical response. 
  For enhancing the versatility  of electrochemical gradients and its possible usage in
different kinds of devices and applications, it is
desirable to predesign GRIN structures with spatial 
predictability of porosity and the corresponding etching rate.  
In this work, we propose a simple model for the calculation of the current
density as a function of position within an electrochemical cell used
to produce porous silicon structures with a controlled gradient in their
index of refraction. The characterization of some typical PS samples with 
lateral porosity and thickness gradient (produced using pin Pt electrode) 
with scanning electron microscopy and
ultraviolet-visible-near infrared reflectance spectroscopy was 
found to be in conformity with the properties predicted through 
the proposed model. In addition,
as the results allow us to obtain the complete dependence of
porosity, dielectric function and the corresponding etching rate for each 
current density from some measurements performed on a single or 
a couple of samples, the proposed model can facilitate the designing 
of novel sensing devices based on surfaces with lateral gradient in refractive indices.}
Keywords: Porous Silicon; GRIN; Reflectance Spectra.
\end{abstract}
\notaL{Cambié el abstract, pero habrá que revisarlo después.}

\section{Introduction}
\label{sec:introduction}
\notaV{
Introduction

Surfaces with gradient in the refractive index (GRIN) are of 
importance not only due to the possibility of being able to 
engineer/tune the propagation of light within the structure’s 
surface for applications such as flat lenses, but also for several 
interesting biological applications where the continual topographical 
variation is being exploited \cite{pierscionek2012gradient}. As an example, 
roughness dependent  response of the cells has been tested on such 
materials for applications in medical implants \cite{bai2020bioinspired}.  
 Gradients have also been employed for several 
technological applications such as high-yield screening of catalysts, 
sensing materials and biomolecules \cite{maier2007combinatorial, jayaraman2004construction, 
potyrailo2008combinatorial}
%[W. F. Maier, K. Stçwe, S. Sieg, Angew. 
%Chem. 2007, 119, 6122; Angew. Chem. Int. Ed. 2007, 46, 6016. ;  S. Jayaraman, 
%A. C. Hillier, J. Comb. Chem. 2004, 6, 27; S. Jayaraman, A. C. Hillier, Meas. 
%Sci. Technol. 2005, 16, 5. ; R. A. Potyrailo, V. M. Mirsky, Chem. Rev. 2008, 108, 770.]
%%
Apart from some methods developed by S.E. Fosdick et al \cite{fosdick2010two},
%[JACS  2010, 132, 9226-9227], 

@@

on gold electrode have been made by Shannon’s group\cite{wang2019fabrication}.  
Among the electrochemical methods, compositional and doping density changes 
in the conducting polymer have been used to produce the gradients using Indium tin 
oxide electrode \cite{inagi2010bipolar}
%[S. Inagi, Y. Ishiguro et al Angew Chem Int. Ed. 2010, 49, 10136-10139;
%Angew Chem 2010 122, 10334-10337].   

@@

reactions and gradient doping of the polymers \cite{qin2020bipolar, ishiguro2011gradient}
%[Gradient Doping of Conducting Polymer 
%Films by Means of Bipolar Electrochemistry Y. Ishiguro, S. Inagi, and T.Fuchigami 
%Langmuir 2011 27 (11), 7158-7162].   (PENDING : few MORE EXAMPLES from last couple of years)

@@

with VLSI devices and integrable with microelectronics, for the fabrication 

@@

electrode configuration in the electrochemical synthesis of porous silicon \cite{sailor2012porous}.  

@@

chemical and biosensor \cite{kumar2020porous},
%[Porous Silicon Fabry–Pérot Interferometer for
%N-Acetyl-β-d-Glucosaminidase Biomarker Monitoring  D. Nanda Kumar, 
%Nofar Pinker, and Giorgi Shtenberg  ACS Sensors 2020 5 (7), 1969-1976; DOI: 
%10.1021/acssensors.0c00348], 
microelectronics and MEMS \cite{martinez2016dual},as well as a 
range of optical \cite{estevez2014porous} and optoelectronic applications
\cite{ramadan2020fabrication}. Specifically, 

@@

\cite{perez2018reflectivity} of 1D photonics crystals. 

@@

with a lateral gradient (in terms of optical thickness/ pore size and thickness 
of the porous layer) has also been exploited for different applications 
\cite{collins2002determining}. In this configuration, a small platinum electrode (cathode)  

@@

density  with an increase in the distance from the electrode
 \cite{khung2008using, clements2011mesenchymal}. 

@@

to  few micrometers  \cite{wang2015screening}. The range of the dimensions of the pores and 

@@

in 2002 \cite{collins2002determining, sailor2012porous} applied it 
for the determination of protein size. 

@@

 optical filters (multilayered structures) with lateral gradient \cite{li2005painting}
% [Li, Yang Yang, Peter Kim, and Michael J. Sailor. 
% "Painting a rainbow on silicon–a simple method to 
% generate a porous silicon band filter gradient.
% " physica status solidi (a) 202.8 (2005): 1616-1618.] 
for developing ethanol sensor (Sailor 2012)\cite{sailor2012porous}. 
 Additionally it has been shown that the combination of thermal  oxidation  and 

@@

optical elements from PS \cite{ocier2017tunable}.    
Kruger et al showed the \cite{krueger2016porous}
%the ...  [ Krueger, Neil A., et al. "Porous silicon gradient 
%refractive index micro-optics." Nano letters 16.12 (2016): 7402-7407.] 
In addition the same group \cite{krueger2018electrochemical}
%[Krueger, Neil A., et al. 
% "Electrochemical Fabrication of Flat, Polymer‐Embedded 
%Porous Silicon 1D Gradient Refractive Index Microlens 
%Arrays." physica status solidi (a) 215.13 (2018): 1800088].  

@@

radial interfacial potential distribution \cite{wang2019fabrication}
%(Wang, Joanna, 
%Michael J. Sailor, and Byoung‐Yong Chang. "Fabrication of a lateral 
%gradient rugate in porous silicon for a miniature spectrometer
%application." ChemElectroChem 6.24 (2019): 5967-5972.
On the other hand, the effect of different topographical
features present on the same chip, has also been 
used to culture / adhesion of certain cells \cite{khung2008using}

@@

evaluated parameters. Finally,  the conclusions are given in Section 5
%$ 
%
}

%\notaV{ $Painting a rainbow on silicon - A simple method to  generate a porous silicon 
%band filter gradient. / Li, Yang Yang; Kim, Peter; Sailor, Michael J.
%In: Physica Status Solidi (A) Applications and Materials Science, 
%Vol. 202, No. 8, 06.2005, p. 1616-1618.  (https://doi.org/10.1002/pssa.200461200)
%
%Electrochemical Preparation of Pore Wall Modification Gradients 
%across Thin Porous Silicon Layers
%Corrina M. Thompson, Michel Nieuwoudt, Anne M. Ruminski, 
%Michael J. Sailor, and Gordon M. Miskelly
%Langmuir 2010 26 (10), 7598-7603
%DOI: 10.1021/la904408h
%
% Richardson, Kathleen A., et al. "Advances in infrared gradient 
% refractive index (GRIN) materials: a review." Optical Engineering 59.11 (2020): 112602.
% 
%
%Lavanant, Enora, et al. "Radial gradient refractive index 
%(GRIN) infrared lens based on spatially resolved crystallization 
%of chalcogenide glass." Optical Materials Express 10.4 (2020): 860-867.
%While widely used in the visible, radial gradient refractive 
%index (GRIN) lenses are still elusive in the IR waveband. 
%In this paper we introduce a new method based on spatially
%resolved crystallization of chalcogenide glass to produce such lenses. 
%Optical and structural
%
%Yoon, Sun Mi, et al. "Subwavelength Hollow-Nanopillared Glass 
%with Gradient Refractive Index for Ultralow Diffuse Reflectance 
%and Antifogging." ACS applied materials & interfaces 12.5 (2020): 6234-6242.
%Nanostructured glass with subwavelength hollow nanopillars 
%of diameters of sub-65 nm was fabricated, showing high optical 
%transmittance and ultralow diffuse reflectance. A simple
%process involving single-step plasma etching was used on a 
%glass slide coated with a SiO2...
%
%Perez, Julius C., Tahmid H. Talukdar, and Judson D. Ryckman. 
%"Patterning Refractive Index on the Surface of a Chip by Direct 
%Nanoimprinting." CLEO: QELS_Fundamental Science. Optical Society of America, 2020.
%
%Szymanowski, Hieronim, et al. "Thin SiNC/SiOC Coatings with a 
%Gradient of Refractive Index Deposited from Organosilicon Precursor." Coatings 10.8 (2020): 794.
%  
%Perez, Julius C., Tahmid H. Talukdar, and Judson D. Ryckman.
% "Patterning Refractive Index on the Surface of a Chip by Direct 
% Nanoimprinting." CLEO: QELS_Fundamental Science. Optical Society of America, 2020.
% $
%}

@@

We assume that our electrolytic cell has the shape of a rectangular
prism (see Fig. \ref{f:celda}) with a horizontal base of sides $a$ and $b$, and
filled with the electrolyte up to a height $c$. We assume that the
walls of the cell are insulating while the bottom is completely
covered with the sample, which is an
electrically grounded relatively good conductor. Within the electrolyte we position an electrode
which we assume is a thin conducting wire, insulated from the electrolyte
but for a small tip, which we approximate as a
point current source.
\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{celdan1.png}
  \caption{Prism shaped electrolytic cell with a rectangular base of
    sides $a$, $b$ filled with electrolyte up to a height $c$. The
    walls of the cell are insulating and the bottom is completely
    covered by the sample, which is assumed to be a good
    conductor. The tip of the electrode is a thin insulated wire
    with just the tip uncovered and located at $\bm r_0=(x_0,y_0,z_0)$ within the
    liquid. The current flows through the electrolyte from the sample
    to the tip.}
  \label{f:celda}
\end{figure}
Within the electrolyte the current density is
\begin{equation}
  \label{eq:j}
  \bm j=\sigma\bm E,
\end{equation}
with
$\sigma$ the conductivity, $\bm E=-\nabla\phi$ the electric field,
and $\phi$ the electric potential. In a
stationary situation
$\nabla\cdot \bm j = \sigma\nabla\cdot\bm E=0$. Thus, the potential
obeys Laplace's equation within the electrolyte,
\begin{equation}
  \label{eq:laplace}
\nabla^{2} \phi=0.
\end{equation}
Consider now an arbitrary closed surface
$\mathcal S$
within the electrolyte that surrounds completely the tip of the
electrode. Integrating $ \bm j$ over this surface we obtain
\begin{equation}
  \label{eq:I}
\int_{\mathcal S'} d\bm a \cdot \bm j = -I,
\end{equation}
where the prime on $\mathcal S'$ means we remove from the surface a
very small hole through which the wire that feeds the current to the
electrode gets
through, and the sign is consistent with the current direction in
Fig. \ref{f:celda}. Assuming the wire is narrower than any other relevant
distance in the system, we may interpret Eq. \eqref{eq:I} as an
integral over a closed surface of the current \eqref{eq:j} within the
electrolyte, ignoring the actual current within the wire. Thus
\begin{equation}
  \label{eq:gauss}
  \int_{\mathcal S} d\bm a \cdot \bm E = -\frac{I}{\sigma}
\end{equation}
Using Gauss's law, we interpret this equation as a source for the
potential in the form of a point charge
\begin{equation}
  q_0 = -\frac{I}{4 \pi \sigma}
\end{equation}
at the position $\bm r_0=(x_0, y_0, z_0)$ of the
tip of the electrode. Note that $q_0$ would be the total charge,
and it shouldn't be further screened through the permittivity of the
electrolyte.

@@

This problem may be solved readily using image charge theory \cite{jackson1999classical}.

@@

The electrostatic potential produced by an infinite array of
charges expressed as a sum in real space of Coulomb terms has ill
convergence properties. The potential can be obtained
using the Ewald summation technique \cite{brodka2004ewald}, which yields
two rapidly converging series, one in real space and another one in reciprocal space.
Nevertheless, as we need the potential and the field to obtain the
current density on the surface of the sample on which  no
real nor image charges lie, we may perform a somewhat simpler planewise
summation, where we first obtain the potential and field produced by a
simple periodic lattice of charges using a fast convergent sum over the 2D
reciprocal vectors \cite{kratzer2019basics}, then sum over the charges that form the basis
of the 2D {\em crystal} plane, and finally sum over all the
 planes \notaC{cite{T6,T7}, esta citas las quite porque no puedo contestar esa pregunta de 
 abajo}.\notaL{¿Estas referencias son relevantes? ¿En verdad
 se define en ellas la suma de Ewald por planos? Dime dónde p.f., en qué
 página. Y checa que todas las referencias tengan que ver con lo que decimos}

@@

In Fig. \ref{fig:DE1} we show a schematic representation of our
experimental setup to manufacture GRIN PS structures.
As dicussed above, we fabricated an electrolytic cell with the shape of a
rectangular prism on the bottom of which we place a Si wafer which makes
electrical contact to a brass \notaC{ laton. gold plate} 
\notaL{Lo inventé; de qué material es
  el contacto bajo la muestra?} which together make the anode. The
cathode consists of a platinum wire insulated except for a small region
at its tip, which we take as a point current drain.
We also show a schematic drawing of the expected GRIN PS structures,
with a gradient in the porosity, and in the thickness, density and depth
of the resulting pores.

\subsection{Fabrication of GRIN  PS Single Layers}
\label{sec:fabrication-ps-grin}
We manufactured single layer PS structures through electrochemical
anodization of a (100) $p$-type crystalline Si wafer
(resistivity 0.002 - 0.005 $ \Omega\,\text{cm}$), under galvanostatic
conditions. The process was performed at
\notaC{room temperature, no controle latempertaura}
,\notaL{OJO. No controlaste la temperatura} with an
electrolytic mixture of aqueous hydrofluoric
acid (HF) (concentration 48\% wt), glycerol (purity 99.8 \% wt) and
ethanol (purity 99.9\% wt) in a 3:7:1 volume ratio. \notaL{Checa que
  todo esto sí corresponda a tus últimas muestras} \notaC{SI corresponde}
   After the anodizing process, the samples were rinsed with
ethanol (purity: 99.9 $ \% $  wt). The electrolytic cell had the shape
of a rectangular prism as shown in Fig. \ref{fig:DE1}, with a base of
sides $a=2.01\,\text{cm}$ \notaL{Cambié el número, de acuerdo a unas
  mediciones de Cristian} and $b=1.48\,\text{cm}$, with an uncovered sample area
of about $3\,\text{cm}^2$. The height of the liquid was set at
$c=1\,\text{cm}$. The cathode was a
platinum wire that with a diameter of $0.41\,\text{mm}$ insulated by a
teflon cylinder of external diameter $\,2\text{mm}$, with an uncovered
tip located at $\bm r_0=(x_0,
y_0,z_0)=(0.2\,\text{cm},0.74\,\text{cm},0.9\,\text{cm})$. \notaL{Checa todos estos datos}
We manufactured three samples $G_1$, $G_2$ and $G_3$ by applying a
current $I_1=5\,\text{mA}$, $I_2=10\,\text{mA}$ and
$I_3=20\,\text{mA}$, respectively, during a time of $t=250s$.

\subsection{Reflectance Measurement}
\label{sec:refl-meas}
We measured the reflectivity spectra at different positions over our
samples using a {\em Perkin Elmer Lambda 950}
UV-Vis-NIR spectrophotometer.\notaL{Finalmente, ¿fue éste el que se
  usó? Si sí, ¿hay algo internesante que decir sobre el? Cosas como el
tamaño de mancha, resolución espectral, etc.} \notaC{Data collection absoluto
reflectance mode. Spot size, physical setting, width (0.7mm) and length (2.0mm).
Instrument setting, slit width (0.6mm). Method settings 
wavelength from(1400nm) to(300nm)}

 For interpretation of the data layer we used
the standard formula \cite{stenzel2015physics} for the reflectance of three media:
air (0) environment, the PS film (1) and the c-Si substrate (2),
 \begin{equation}\label{Eq:ECMR}
   R=\left |\frac{r _ {_ {01}}r _ {_ {12}} e^{2i\psi}}{1+r _ {_
   {01}}r _ {_ {12}} e^{2i\psi}}\right |^2
\end{equation}
where $r_{01}$ and $r_{12}$ are the Fresnel reflectance
coefficients of the air/PS and PS/c-Si interfaces \cite{sattler2017silicon}
and $\psi=k_1^\perp d$, where $k_1^\perp$ is
the component of the wavevector perpendicular to the surface within
the porous layer of thickness $d$. The reflectance depends on the
thickness of the film and on the index of refraction $n_1=n_{\text{PS}}$ of the porous
layer, which we relate to the porosity through Bruggeman's
effective medium theory \cite{theiss1997optical},
\begin{equation}\label{Eq:Brugg}
 p\frac{1-\epsilon_1} {1+\epsilon_1} + (1-p)
  \frac{\epsilon_2 - \epsilon_1}
  {\epsilon_2+\epsilon_1}=0,
\end{equation}
where $\epsilon_2=\epsilon_{\text{Si}}$ is the dielectric function of
the c-Si substrate, and
$\epsilon_1=n_{\text{PS}}^2$ is the dielectric function of the PS layer.
We fitted the reflectance spectra using the porosity $p$ and the
thickness $d$ and a scale calibration factor $s$ as fitting
parameters, and thus, we obtained the porosity
$p$ and the etching rate $v=d/t$ for different values of the local
current density $j_\perp$ expected at several positions on different
samples.
